---
title: "Canada Inflation Project"
output: pdf_document
date: "2024-05-25"
---

# Import Libraries

```{r }
import_libraries <- function(){
library(fpp3)
library(fabletools)
library(zoo)
library(tseries)
library(quantmod) # download data form Yahoo finance
library(moments) # to know summary statistics of data
library(tinytex)
library(forecast)
library(tsintermittent)
library(expsmooth)
library(readxl)
library(dplyr)
library(tsibble)
library(ggplot2)
library(fable.prophet) 
library(prophet)
library(fable.prophet)
library(tools)
library(Hmisc)
library(corrplot)
library(ISLR)
library(ggplot2)
library(GGally)
library(e1071)
library(randomForest)
library(xts)
#install.packages("mass")
}

#******************************************************************************#
# Read Excel/CSV File
read_file <- function(name){
  if (file_ext(name)=="xls"){
    data <- read_excel(name)
  }
  else{
    data <- read_csv(name)
  }
  return(data)
}
#******************************************************************************#
# Sign Correlation
rho.cal<-function(X){
  rho.hat<- cor(X-mean(X), sign(X-mean(X)))
  return(as.numeric(rho.hat))
}

#******************************************************************************#
# Split Dataset into Train and Test Dataset
split <- function(data,a,b)
  {
# Train Dataset
#mutate(bcpi_p =  ((bcpi - lag(bcpi))/lag(bcpi)) * 100)
train_dataset <- data %>% filter(Date>"1986-01-30" & Date<=a)
# Test Dataset
test_dataset <- data %>% filter(Date>a & Date<=b)
return(list(c=train_dataset, d=test_dataset))
}

#******************************************************************************#
# Convert data into timeseries dataset
convert_ts_obj <- function(data)
{
# Create date variable
ts_data <- zoo::fortify.zoo(data)
ts_data <- as_tsibble(ts_data, index = Index) # create tissble object
ts_data <- ts_data |>
mutate(month = row_number()) |>
update_tsibble(index = month, regular = TRUE)
return(ts_data )
}

#******************************************************************************#
# Plot Forecast
plot_forecast <- function(forecast,data,test_data){
# Plot the forecasts with whole data
print(forecast |>
  autoplot(data)+ 
  labs(y = "% Change From Year Ago",
       x = "Months after 1/1/1972",
       title = "Inflation Rate Forecast : Canada"))
 
#Plot only forecast period        
print(forecast |>
  autoplot(test_data) + 
  labs(y = "% Change From Year Ago",
        x = "Months after 1/1/1972",
       title = "Inflation Rate Forecast : Canada"))
}

#******************************************************************************#
# benchmark models (mean, naive, drift)
benchmark <- function(data,train_data,test_data){
ben_fit <- train_data |>
  model(
    #Mean = MEAN(cpi),
    #Naïve = NAIVE(cpi),
    Drift = RW(cpi ~ drift())
  )

# forecast
ben_fc <- ben_fit |> forecast(test_data)

# Plot Forecast
plot_forecast(ben_fc,data,test_data)

#Portmanteau tests for autocorrelation
# Test for drift Method
fit <- train_data |> model(RW(cpi ~ drift()))
#tidy(fit)
print(augment(fit) |> features(.innov, ljung_box, lag=25))
#Residual check
print(fit |>gg_tsresiduals())

#Accuracy()
accuracy.ben <-  accuracy(ben_fc,data)
return(accuracy.ben)
}

#******************************************************************************#
# Arima Model
arima <- function(data,train_data,test_data){
arima_fit <- train_data |> model(arima = ARIMA(cpi))
#ets = ETS(CPI_Index)
#prophet = prophet(cpi)
  report(arima_fit) 

# forecast
arima_fc <- arima_fit |> forecast(test_data)

# Plot Forecast
plot_forecast(arima_fc ,data,test_data)

#Portmanteau tests for autocorrelation
# Test for drift Method
print(augment(arima_fit) |> features(.innov, ljung_box, lag=25))
#Residual check
print(arima_fit  |>gg_tsresiduals())

#Accuracy()
accuracy.arima <-  accuracy(arima_fc,data)
return(accuracy.arima )
}

#******************************************************************************#

# Neural Network Model without Covariates
nnar<- function(data,train_data,test_data){
nnar_fit <- train_data |> model( N1=  NNETAR((cpi)))
#ets = ETS(CPI_Index)
#prophet = prophet(cpi)
report(nnar_fit) 

# forecast
nnar_fc <- nnar_fit |> forecast(test_data)

# Plot Forecast
plot_forecast(nnar_fc ,data,test_data)

#Portmanteau tests for autocorrelation
# Test for drift Method
print(augment(nnar_fit) |> features(.innov, ljung_box, lag=25))
#Residual check
print(nnar_fit  |>gg_tsresiduals())

#Accuracy()
accuracy.nnar <-  accuracy(nnar_fc,data)
return(accuracy.nnar )
}

#******************************************************************************#
# Neural Network Model with Covariates
nnar_covar <- function(data,train_data,test_data){
nnar_fit <- train_data |> model( N2=  NNETAR((cpi ~ exchange_rate + oil_price + money_supply  + interest_rate + bcpi + I(unemp_rate)^2)))
#ets = ETS(CPI_Index)
#prophet = prophet(cpi)
report(nnar_fit) 

# forecast
nnar_fc <- nnar_fit |> forecast(test_data)

# Plot Forecast
plot_forecast(nnar_fc ,data,test_data)

#Portmanteau tests for autocorrelation
# Test for drift Method
print(augment(nnar_fit) |> features(.innov, ljung_box, lag=25))
#Residual check
print(nnar_fit  |>gg_tsresiduals())

#Accuracy()
accuracy.nnar <-  accuracy(nnar_fc,data)
return(accuracy.nnar )
}

#******************************************************************************#
combination1 <- function(data,train_data,test_data){
combine1 <- train_inflation %>% model(
  Dynamic = ARIMA(cpi ~ exchange_rate + oil_price + money_supply  + interest_rate + bcpi + I(unemp_rate)^2),
  Neural_Network =  NNETAR((cpi)),
  N2 = (NNETAR(cpi ~ exchange_rate + oil_price + money_supply  + interest_rate + bcpi + I(unemp_rate)^2))
) %>% 
mutate( Combination=(Dynamic+ Neural_Network + N2)/3 ) 

#Forecast

fc_combine <- forecast(combine1, test_inflation) 

# Plot the forecasts with whole data
fc_combine %>%  autoplot(inflation)+ 
  labs(y = "% Change From Year Ago",
       x = "Months after 1/1/1972",
       title = "CPI Index Forecast : Canada",
       subtitle = "(Jan 1972 - Aug 2023)") 

#Plot only forecast period  
fc_combine %>%  autoplot(test_inflation)+ 
  labs(y = "% Change From Year Ago",
        x = "Months after 1/1/1972",
       title = "CPI Index Forecast : Canada",
       subtitle = "(Sept 2022 - Aug 2023)")


#Accuracy
accuracy.hm <- accuracy(fc_combine,inflation)
accuracy.hm
}
#******************************************************************************#

# Timeseries model 
timeseries <- function(data,train_data,test_data){
ts_fit <- train_data |> model( lm = TSLM(cpi ~ exchange_rate+ oil_price + money_supply + interest_rate + bcpi  + I(unemp_rate)^2))
#ets = ETS(CPI_Index)
#prophet = prophet(cpi)
report(ts_fit) 

# forecast
ts_fc <- ts_fit  |> forecast(test_data)

# Plot Forecast
plot_forecast(ts_fc ,data,test_data)

#Portmanteau tests for autocorrelation
# Test for drift Method
print(augment(ts_fit) |> features(.innov, ljung_box, lag=25))
#Residual check
print(ts_fit  |>gg_tsresiduals())

#Accuracy()
accuracy.ts <-  accuracy(ts_fc,data)
return(accuracy.ts )
}

#******************************************************************************#
# Dynamic model 
dyn_reg <- function(data,train_data,test_data){
dyn_fit <- train_data |> model( ARIMA(cpi ~ exchange_rate + oil_price + money_supply  + interest_rate + bcpi + I(unemp_rate)^2))
report(dyn_fit) 

# forecast
dyn_fc <- dyn_fit  |> forecast(test_data)

# Plot Forecast
plot_forecast(dyn_fc ,data,test_data)

#Portmanteau tests for autocorrelation
# Test for drift Method
print(augment(dyn_fit) |> features(.innov, ljung_box, lag=25))
#Residual check
print(dyn_fit  |>gg_tsresiduals())

#Accuracy()
accuracy.dyn <-  accuracy(dyn_fc,data)
return(accuracy.dyn )
}

#******************************************************************************#
# ETS Model
ets_model <- function(data,train_data,test_data){
ets_fit <- train_data |> model(ets = ETS(cpi))
#prophet = prophet(cpi)
  report(ets_fit) 

# forecast
ets_fc <- ets_fit |> forecast(test_data)

# Plot Forecast
plot_forecast(ets_fc ,data,test_data)

#Portmanteau tests for autocorrelation
# Test for drift Method
print(augment(ets_fit) |> features(.innov, ljung_box, lag=25))
#Residual check
print(ets_fit  |>gg_tsresiduals())

#Accuracy()
accuracy.ets <-  accuracy(ets_fc,data)
return(accuracy.ets)
}

#******************************************************************************#

```

# Load File

```{r }
# Import Libraries
import_libraries()

# Read File
can_inf_data <- read_file("inflation_new.xls")

# Exploratory Data Analysis
#view(data)
cat("Column Names are:", paste(colnames(can_inf_data), collapse = ", "))
cat("\n")
cat("Dimensions are:", paste(dim(can_inf_data)))
print(head(can_inf_data))
print(head(can_inf_data))

# Check Missing Value
print(sapply(can_inf_data, function(x) sum(is.na(x))))

#OUTLIER#***********************************************************************
# tsoutliers(can_inf_data$cpi)
# 
# tsoutliers(can_inf_data$interest_rate)
# # Extract the outlier indices and replacement values
# outlier_indices <- c(113, 114, 115, 116, 117)
# replacement_values <- c(17.55, 17.70, 17.85, 18.00, 18.15)
# # Replace outliers with specified replacement values
# can_inf_data$interest_rate[outlier_indices] <- replacement_values
# 
# tsoutliers(can_inf_data$money_supply)
# # Extract the outlier indices and replacement values
# outlier_indices1 <- c(29, 32, 33)
# replacement_values1 <- c(25.45704, 26.27413, 26.00447)
# # Replace outliers with specified replacement values
# can_inf_data$money_supply[outlier_indices1] <- replacement_values1
# 
# tsoutliers(can_inf_data$exchange_rate)
# # Extract the outlier indices and replacement values
# outlier_indices2 <- c(442, 443, 444, 445, 446, 447, 448, 459)
# replacement_values2 <- c(-6.836283, -7.151235, -7.466188, -7.781140, -8.096093, -8.411045, -8.725998, 19.163995)
# # Replace outliers with specified replacement values
# can_inf_data$exchange_rate[outlier_indices2] <- replacement_values2
# 
# tsoutliers(can_inf_data$unemp_rate)
# # Extract the outlier indices and replacement values
# outlier_indices3 <- c(42, 126, 127, 128, 129, 130, 131, 132, 133, 450, 451, 452, 579, 580, 581, 582, 583, 584, 585, 586, 587, 588, 589, 590, 592, 593, 594, 618, 619)
# replacement_values3 <- c(32.461875, 43.015679, 42.975798, 42.935917, 42.896036, 42.856154, 42.816273, 42.776392, 42.736511, 37.762417, 36.815155, 35.867893, -2.324115, -2.924089, -3.524064, -4.124038, -4.724013, -5.323988, -5.923962, -6.523937, -7.123912, -7.723886, -8.323861, -8.923835, -15.097402, -20.670995, -26.244588, 1.257860, 2.515720)
# # Replace outliers with specified replacement values
# can_inf_data$unemp_rate[outlier_indices3] <- replacement_values3
# 
# tsoutliers(can_inf_data$oil_price)
# # Extract the outlier indices and replacement values
# outlier_indices4 <- c(25, 26, 27, 28, 29, 30, 31, 592)
# replacement_values4 <- c(35.25534, 49.44326, 63.63118, 77.81910, 92.00701, 106.19493, 120.38285, 120.78605)
# # Replace outliers with specified replacement values
# can_inf_data$oil_price[outlier_indices4] <- replacement_values4
# 
# tsoutliers(can_inf_data$bcpi)
# # Extract the outlier indices and replacement values
# outlier_indices5 <- c(405, 434, 435, 436, 437, 438, 439, 440, 441, 443, 444, 445, 446, 447, 448, 449, 451, 453, 472, 508, 509, 510, 511, 528, 529, 530, 579, 580, 581, 582, 583, 585, 586, 587, 601, 602, 603, 604, 605, 606, 607, 608, 617, 618, 619)
# replacement_values5 <- c(561.4200, 637.3400, 625.9000, 614.4600, 603.0200, 591.5800, 580.1400, 568.7000, 557.2600, 539.0688, 532.3175, 525.5663, 518.8150, 512.0638, 505.3125, 498.5613, 488.1400, 496.1350, 684.7100, 631.9280, 628.3360, 624.7440, 621.1520, 339.4275, 336.0050, 332.5825, 397.4967, 400.5133, 403.5300, 406.5467, 409.5633, 420.7200, 428.8600, 437.0000, 644.7433, 649.4567, 654.1700, 658.8833, 663.5967, 668.3100, 673.0233, 677.7367, 631.8500, 629.9800, 628.1100)
# # Replace outliers with specified replacement values
# can_inf_data$bcpi[outlier_indices5] <- replacement_values5

#################################################################################
# Trend of the Inflation Rate
can_inf_data |>
  ggplot(aes(y = cpi, x = Date)) +
  geom_line(col='blue') +
  labs(y = "% Change of CPI",
       x = "Year",
       title = "Monthly Inflation Rate Over Time",
       subtitle = "(Jan 1972 - Aug 2023)")

# Check Distribution of the Data
print(ggplot(data = can_inf_data, aes(x = cpi)) +
  geom_histogram(bins=50,fill = "lightblue", color = "blue") +
  labs(title = "Canada Inflation Rate Distribution",
       x="Inflation Rate",
       y="Frequency"))

# summary of the whole Dataset
summary(can_inf_data)

# Compute correlation matrix
correlation_matrix <- rcorr(as.matrix(can_inf_data[2:8]))
print(correlation_matrix$r)
corrplot(correlation_matrix$r, method = "color")

# Create a scatterplot matrix using GGally
selected_columns <-can_inf_data[, 2:8]
print(ggpairs(selected_columns, progress = FALSE) +
  theme_bw())

# Scale Data
inf_scaled <- scale(can_inf_data[2:8])
inf <- cbind(can_inf_data[1],inf_scaled)

# Check Outliers
#tsoutliers(inflation$cpi)
# Select the desired columns
selected_columns <- c("cpi","interest_rate","money_supply","exchange_rate","unemp_rate","oil_price","bcpi")
subset_data <- inf[, selected_columns]
# Create a long-form data frame for boxplots
subset_data_long <- tidyr::gather(subset_data, key = "Variable", value = "Value")
# Create a boxplot using ggplot2
print(ggplot(subset_data_long, aes(x = Variable, y = Value)) +
  geom_boxplot(fill = "lightblue", color = "black") +
  labs(x = "Variable", y = "Value") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("Boxplots for All Variables"))

```

* There are no missing values in the inflation dataset. I didnot replace outlier from external values with any values. So outlier part is commented.

* I extracted from excel file and saved into can_inf_data. Then I converted this to tsibble object by calling below function.

* (If you want to try for scaled dataset, you can do it with inf variable which have scaled data. In this scenario, instead of "can_inf_data", you need to use inf to make it tsible object)

## Convert to tsibble object

```{r }
inflation <- convert_ts_obj(can_inf_data)
head(inflation)
tail(inflation)
```

# Model FITTING

* I want to perform Rolling window Cross Validation for h=1/3/6/12. For this I used window_size=540
* This dataset has data Jan 1972 to Aug 2023 (620)
* {Training dataset} - January 1972 to December 2016 (540)
* {Testing dataset} - January 2017 to August 2023 (80)
* I performed forecast for h=1/3/6/12 
* For h=1, will get 80 forecast values; for h=2 will get 78 forecasts, for h=3 will get 75 forecasts and for h=12 will get 69 forecasts.

** I used name cpi everyehere, but its inflation rate.**

## True values of cpi

```{r}
# Define the test data for different forecasting horizons
test_data_h1 <- inflation[541:620, ]  # h = 1
test_data_h3 <- inflation[543:620, ]  # h = 3
test_data_h6 <- inflation[546:620, ]  # h = 6
test_data_h12 <- inflation[552:620, ] # h = 12

# Extract the actual CPI values
actual_cpi_h1 <- test_data_h1$cpi
actual_cpi_h3 <- test_data_h3$cpi
actual_cpi_h6 <- test_data_h6$cpi
actual_cpi_h12 <- test_data_h12$cpi

# Store actual_cpi_h1, actual_cpi_h3, actual_cpi_h6, and actual_cpi_h12 in true_values
true_values <- list(
  `1` = actual_cpi_h1,
  `3` = actual_cpi_h3,
  `6` = actual_cpi_h6,
  `12` = actual_cpi_h12
)
```

## Arima Forecast h=1/3/6/12 

```{r }
#inflation <- inflation %>% filter(Date >= "1985-01-01")

# Parameters
arima_window_size <- 540
arima_p <- 0
arima_d <- 1
arima_q <- 0
arima_weightage <- 1
arima_forecast_horizons <- c(1, 3, 6, 12)

# Initialize lists to store forecasts and MSE
arima_forecasts <- list()
arima_mse_list <- c()

# Iterate over each forecast horizon
for (arima_h in arima_forecast_horizons) {
  arima_forecast_values <- c()
  arima_mse_values <- c()
  
  # Iterate over the data
  for (arima_i in 1:(length(inflation$cpi) - arima_window_size - arima_h + 1)) {
    # Extract current window of data
    arima_window_data <- inflation$cpi[arima_i:(arima_i + arima_window_size - 1)]
    
    # Fit ARIMA model to window data
    arima_model <- Arima(arima_window_data, order = c(arima_p, arima_d, arima_q))
    
    # Give weightage to recent values
    arima_forecast <- forecast(arima_model, h = arima_h)$mean * arima_weightage
   
    # Only consider the last forecast value for the specified horizon
    arima_forecast_value <- arima_forecast[length(arima_forecast)]
    arima_forecast_values <- c(arima_forecast_values, arima_forecast_value)
    
    # Calculate actual value
    arima_actual_value <- inflation$cpi[arima_i + arima_window_size + arima_h - 1]
    
    # Calculate MSE
    arima_mse_value <- (arima_forecast_value - arima_actual_value)^2
    arima_mse_values <- c(arima_mse_values, arima_mse_value)
  }
  
  # Store forecasts and MSE for current horizon
  arima_forecasts[[as.character(arima_h)]] <- arima_forecast_values
  arima_mse_list <- c(arima_mse_list, sqrt(mean(arima_mse_values)))
}

# Plot forecasts
par(mfrow = c(2, 2), mar = c(5, 5, 4, 2) + 0.1)
for (arima_h in arima_forecast_horizons) {
  plot(arima_forecasts[[as.character(arima_h)]], type = "l", col = "red", ylim = range(inflation$cpi), 
       xlab = "Observation", ylab = "CPI", main = paste("ARIMA Forecast for h =", arima_h))
  lines(inflation$cpi[(arima_window_size + arima_h):(length(inflation$cpi) )], col = "black")
}

# Print MSE for each horizon
for (arima_i in 1:length(arima_forecast_horizons)) {
  cat("MSE for h =", arima_forecast_horizons[arima_i], ":", arima_mse_list[arima_i], "\n")
}

# I calculated below accuracy, just to verify my above code.
accuracy(arima_forecasts$`1`,true_values$`1`)
accuracy(arima_forecasts$`3`,true_values$`3`)
accuracy(arima_forecasts$`6`,true_values$`6`)
accuracy(arima_forecasts$`12`,true_values$`12`)
```
* Here I used Arima(0,1,0) (even if I dont used p,d,q; it automatically selects (p=0, d=1, q=0) and it takes little more time to run, so I initially mentioned p,d,q values).

* I am not provoding code for Naive as it is giving same forecast as Arima(0,1,0). It is also mentioned that ARIMA(0,1,0) model is indeed a naive model.

## Dynamic Regression Forecast h=1/3/6/12 

```{r}
library(forecast)
#inflation <- inflation %>% filter(Date >="1999-12-01")
# Parameters
dyn_window_size <- 540
dyn_weightage <- 1
dyn_forecast_horizons <- c(1,3,6,12)

# Initialize lists to store forecasts and MSE
dyn_forecasts <- list()
dyn_mse_list <- c()

# Iterate over each forecast horizon
for (dyn_h in dyn_forecast_horizons) {
  dyn_forecast_values <- c()
  dyn_mse_values <- c()
  
  # Iterate over the data
  for (dyn_i in 1:(length(inflation$cpi) - dyn_window_size - dyn_h + 1)) {
    # Extract current window of data
    dyn_window_data <- inflation[dyn_i:(dyn_i + dyn_window_size - 1), ]
    
    # Extract test data
    dyn_test_data <- inflation[(dyn_i + dyn_window_size):(dyn_i + dyn_window_size + dyn_h - 1), ]
    
    # Fit ARIMAX model with external regressors using the window data
    dyn_model <- dyn_window_data |> model(ARIMA(cpi ~ exchange_rate + oil_price + money_supply + interest_rate + bcpi + I(unemp_rate)^2))
    
    # Forecast for the specified horizon with weightage
    dyn_forecast <- forecast(dyn_model, dyn_test_data)$.mean # Only forecasting for h = 1 here
    
    # Store the forecast value
    dyn_forecast_value <- dyn_forecast[length(dyn_forecast)]
    dyn_forecast_values <- c(dyn_forecast_values, dyn_forecast_value)
    
    # Calculate actual value
    dyn_actual_value <- inflation$cpi[dyn_i + dyn_window_size + dyn_h - 1]
    
    # Calculate MSE
    dyn_mse_value <-(dyn_forecast - dyn_actual_value)^2
    dyn_mse_values <- c(dyn_mse_values, dyn_mse_value)
  }
  
  # Store forecasts and MSE for current horizon
  dyn_forecasts[[as.character(dyn_h)]] <- dyn_forecast_values
  dyn_mse_list <- c(dyn_mse_list,  sqrt(mean(dyn_mse_values)))
}

# Plot forecasts for each horizon
par(mfrow = c(2, 2), mar = c(5, 5, 4, 2) + 0.1)
for (dyn_h in dyn_forecast_horizons) {
  plot(dyn_forecasts[[as.character(dyn_h)]], type = "l", col = "red", ylim = range(inflation$cpi), 
       xlab = "Observation", ylab = "CPI", main = paste("Forecast for h =", dyn_h))
  lines(inflation$cpi[(dyn_window_size + dyn_h):(length(inflation$cpi) )], col = "black")
}
#legend("topright", legend = c("Forecast", "Actual"), col = c("red", "black"), lty = 1)
# Print MSE for each horizon
for (dyn_i in 1:length(dyn_forecast_horizons)) {
  cat("MSE for h =", dyn_forecast_horizons[dyn_i], ":", dyn_mse_list[dyn_i], "\n")
}

accuracy(dyn_forecasts$`1`,true_values$`1`)
accuracy(dyn_forecasts$`3`,true_values$`3`)
accuracy(dyn_forecasts$`6`,true_values$`6`)
accuracy(dyn_forecasts$`12`,true_values$`12`)
```

##  NNAR  h=1/3/6/12

* This model takes time to run but not that much. However NNAR with external variables is time taking so you can run both neural network model by planning :P.

```{r}
# Load required library
library(forecast)

# Parameters
nnar_window_size <- 540
nnar_forecast_horizons <- c(1, 3, 6, 12)
nnar_weightage <- 1

# Initialize lists to store forecasts and MSE
nnar_forecasts <- list()
nnar_mse_list <- c()

# Iterate over each forecast horizon
for (nnar_h in nnar_forecast_horizons) {
  nnar_forecast_values <- c()
  nnar_mse_values <- c()
  
  # Iterate over the data
  for (nnar_i in 1:(length(inflation$cpi) - nnar_window_size - nnar_h + 1)) {
    # Extract current window of data
    nnar_window_data <- inflation$cpi[nnar_i:(nnar_i + nnar_window_size - 1)]
    
    # Fit nnar model to window data
    nnar_model <- nnetar(nnar_window_data)
    
    # Give weightage to recent values
    nnar_forecast <- forecast(nnar_model, h = nnar_h)$mean * nnar_weightage
    
    # Only consider the last forecast value for the specified horizon
    nnar_forecast_value <- nnar_forecast[length(nnar_forecast)]
    nnar_forecast_values <- c(nnar_forecast_values, nnar_forecast_value)
    
    # Calculate actual value
    nnar_actual_value <- inflation$cpi[nnar_i + nnar_window_size + nnar_h - 1]
    
    # Calculate MSE
    nnar_mse_value <- (nnar_forecast_value - nnar_actual_value)^2
    nnar_mse_values <- c(nnar_mse_values, nnar_mse_value)
    
    if (nnar_h == 1) {
      nnar_forecasts[[as.character(nnar_h)]] <- nnar_forecast_values
    } else if (nnar_h == 3) {
      nnar_forecasts[[as.character(nnar_h)]] <- nnar_forecast_values
    } else if (nnar_h == 6) {
      nnar_forecasts[[as.character(nnar_h)]] <- nnar_forecast_values
    } else if (nnar_h == 12) {
      nnar_forecasts[[as.character(nnar_h)]] <- nnar_forecast_values
    }
  }
  
  nnar_mse_list <- c(nnar_mse_list, sqrt(mean(nnar_mse_values)))
}

# Plot forecasts for each horizon
par(mfrow = c(2, 2), mar = c(5, 5, 4, 2) + 0.1)
for (nnar_h in nnar_forecast_horizons) {
  plot(nnar_forecasts[[as.character(nnar_h)]], type = "l", col = "red", ylim = range(inflation$cpi), xlab = "Observation", ylab = "CPI", main = paste("NNAR Forecast for h =", nnar_h))
  lines(inflation$cpi[(nnar_window_size + nnar_h):(length(inflation$cpi))], col = "black")
  #legend("topright", legend = c("Forecast", "Actual"), col = c("blue", "red"), lty = 1)
}

# Print MSE for each horizon
for (nnar_i in 1:length(nnar_forecast_horizons)) {
  cat("MSE for h =", nnar_forecast_horizons[nnar_i], ":", nnar_mse_list[nnar_i], "\n")
}

accuracy(nnar_forecasts$`1`,true_values$`1`)
accuracy(nnar_forecasts$`3`,true_values$`3`)
accuracy(nnar_forecasts$`6`,true_values$`6`)
accuracy(nnar_forecasts$`12`,true_values$`12`)

```

## NNAR with external variables  h=1/3/6/12 

```{r}
library(forecast)

# Parameters
nnarx_window_size <- 540
nnarx_weightage <- 1
nnarx_forecast_horizons <- c(1,3,6,12)

# Initialize lists to store forecasts and MSE
nnarx_forecasts <- list()
nnarx_mse_list <- c()

# Iterate over each forecast horizon
for (nnarx_h in nnarx_forecast_horizons) {
  nnarx_forecast_values <- c()
  nnarx_mse_values <- c()
  
  # Iterate over the data
  for (nnarx_i in 1:(length(inflation$cpi) - nnarx_window_size - nnarx_h + 1)) {
    # Extract current window of data
    nnarx_window_data <- inflation[nnarx_i:(nnarx_i + nnarx_window_size - 1), ]
    
    # Extract test data
    nnarx_test_data <- inflation[(nnarx_i + nnarx_window_size):(nnarx_i + nnarx_window_size + nnarx_h - 1), ]
    
    # Fit ARIMAX model with external regressors using the window data
    nnarx_model <- nnarx_window_data |> model(NNETAR(cpi ~ exchange_rate + oil_price + money_supply + interest_rate + bcpi + I(unemp_rate)))
    
    # Forecast for the specified horizon with weightage
    nnarx_forecast <- forecast(nnarx_model, nnarx_test_data)$.mean * nnarx_weightage # Only forecasting for h = 1 here
    
    # Store the forecast value
    nnarx_forecast_value <- nnarx_forecast[length(nnarx_forecast)]
    nnarx_forecast_values <- c(nnarx_forecast_values, nnarx_forecast_value)
    
    # Calculate actual value
    nnarx_actual_value <- inflation$cpi[nnarx_i + nnarx_window_size + nnarx_h - 1]
    
    # Calculate MSE
    nnarx_mse_value <-(nnarx_forecast - nnarx_actual_value)^2
    nnarx_mse_values <- c(nnarx_mse_values, nnarx_mse_value)
  }
  
  # Store forecasts and MSE for current horizon
  nnarx_forecasts[[as.character(nnarx_h)]] <- nnarx_forecast_values
  nnarx_mse_list <- c(nnarx_mse_list,  sqrt(mean(nnarx_mse_values)))
}

# Plot forecasts for each horizon
par(mfrow = c(2, 2), mar = c(5, 5, 4, 2) + 0.1)
for (nnarx_h in nnarx_forecast_horizons) {
  plot(nnarx_forecasts[[as.character(nnarx_h)]], type = "l", col = "red", ylim = range(inflation$cpi), 
       xlab = "Observation", ylab = "CPI", main = paste("Forecast for h =", nnarx_h))
  lines(inflation$cpi[(nnarx_window_size + nnarx_h):(length(inflation$cpi) )], col = "black")
}

# Print MSE for each horizon
for (nnarx_i in 1:length(nnarx_forecast_horizons)) {
  cat("MSE for h =", nnarx_forecast_horizons[nnarx_i], ":", nnarx_mse_list[nnarx_i], "\n")
}

accuracy(nnarx_forecasts$`1`,true_values$`1`)
accuracy(nnarx_forecasts$`3`,true_values$`3`)
accuracy(nnarx_forecasts$`6`,true_values$`6`)
accuracy(nnarx_forecasts$`12`,true_values$`12`)
```

## RANDOM FOREST 

* As Random Forest is can not be implemented directly on the data. I included 6 lagged values as predictor in the dataset.
* Therefore for different horizon dataset will be differet and hence I calculated RMSE value by taking different dataset for the resepective horizon.
* I used caret package for Random Forest.
* In this model, I will get Rsquared as NaN as I am using method="timeslice".

### RF Caret  h=1

```{r}
# Load required libraries
library(caret)
library(randomForest)
library(dplyr)

# Create lag features for time series data
h1_lags <- 1:6  # Number of lags to consider for horizon 1
# Create lagged features for the CPI column
h1_lagged_data <- cbind(sapply(h1_lags, function(l) lag(inflation$cpi, l))) # Create lagged data

# Combine the lagged features into one data frame
h1_lagged_df <- data.frame(h1_lagged_data)
colnames(h1_lagged_df) <- paste0("h1_lag_", h1_lags)  # Rename columns with lag prefixes

# Merge the lagged features with the original data
h1_final_data <- bind_cols(inflation, h1_lagged_df)  # Combine data frames

# Remove rows with NAs created by lagging
h1_final_data <- h1_final_data[complete.cases(h1_final_data), ]

# Define the forecasting horizon
forecast_horizon <- 1

train_inflation <- h1_final_data %>% filter(Date <= '2016-12-28')
missing_values <- sum(is.na(train_inflation))
# Want last 80 forecast to compare with other models
test_inflation <- h1_final_data %>% filter(Date >= '2016-12-28' & Date <= '2023-08-28')

# Define the time control for time series cross-validation
myTimeControl <- trainControl(
  method = "timeslice",
  initialWindow = 500,
  horizon = forecast_horizon,
  fixedWindow = TRUE,
  allowParallel = TRUE
)

# Define the formula for the model
formula <- as.formula("cpi ~ . - Date - Index - month")

# Train the Random Forest model
rf_model <- train(
  formula,
  data = train_inflation,
  method = "rf",
  trControl = myTimeControl,
  tuneGrid = expand.grid(mtry = 4),  # Adjust tuning parameters as needed
  metric = "RMSE",
  ntree = 100 
)

# Get forecasted values
rf_forecast1 <- predict(rf_model, newdata = test_inflation)

# Print Accuracy
accuracy(rf_forecast1,test_inflation$cpi)

# Calculate RMSE
rf_RMSE_h1 <- sqrt(mean((rf_forecast1 - test_inflation$cpi)^2))

# Print RMSE
print(paste("RMSE:", rf_RMSE_h1))
plot(test_inflation$cpi, type = "l")
lines(rf_forecast1, col = "red")

```
### RF Caret h=3

```{r}
# Load required libraries
library(caret)
library(randomForest)
library(dplyr)

# Create lag features for time series data for horizon 3
h3_lags <- 3:8  # Number of lags to consider for horizon 3
# Create lagged features for the CPI column
h3_lagged_data <- cbind(sapply(h3_lags, function(l) lag(inflation$cpi, l))) # Create lagged data

# Combine the lagged features into one data frame
h3_lagged_df <- data.frame(h3_lagged_data)
colnames(h3_lagged_df) <- paste0("h3_lag_", h3_lags)  # Rename columns with lag prefixes

# Merge the lagged features with the original data
h3_final_data <- bind_cols(inflation, h3_lagged_df)  # Combine data frames

# Remove rows with NAs created by lagging
h3_final_data <- h3_final_data[complete.cases(h3_final_data), ]

# Define the forecasting horizon
forecast_horizon <- 3  # Update to horizon 3

train_inflation <- h3_final_data %>% filter(Date <= '2016-12-28')
missing_values <- sum(is.na(train_inflation))
# Want last 80 forecast to compare with other models
test_inflation <- h3_final_data %>% filter(Date >= '2017-02-28' & Date <= '2023-08-28')

# Define the time control for time series cross-validation
myTimeControl <- trainControl(
  method = "timeslice",
  initialWindow = 500,
  horizon = forecast_horizon,
  fixedWindow = TRUE,
  allowParallel = TRUE
)

# Define the formula for the model
formula <- as.formula("cpi ~ . - Date - Index - month")

# Train the Random Forest model
rf_model <- train(
  formula,
  data = train_inflation,
  method = "rf",
  trControl = myTimeControl,
  tuneGrid = expand.grid(mtry = 4),  # Adjust tuning parameters as needed
  metric = "RMSE",
  ntree = 100 
)

# Get forecasted values
rf_forecast3 <- predict(rf_model, newdata = test_inflation)

# Print Accuracy
accuracy(rf_forecast3,test_inflation$cpi)

# Calculate RMSE
rf_RMSE_h3 <- sqrt(mean((rf_forecast3 - test_inflation$cpi)^2))

# Print RMSE
print(paste("RMSE:", rf_RMSE_h3))
plot(test_inflation$cpi, type = "l")
lines(rf_forecast3, col = "red")

```
### RF Caret h=6

```{r}
# Load required libraries
library(caret)
library(randomForest)
library(dplyr)

# Create lag features for time series data for horizon 6
h6_lags <- 6:11  # Number of lags to consider for horizon 6
# Create lagged features for the CPI column
h6_lagged_data <- cbind(sapply(h6_lags, function(l) lag(inflation$cpi, l))) # Create lagged data

# Combine the lagged features into one data frame
h6_lagged_df <- data.frame(h6_lagged_data)
colnames(h6_lagged_df) <- paste0("h6_lag_", h6_lags)  # Rename columns with lag prefixes

# Merge the lagged features with the original data
h6_final_data <- bind_cols(inflation, h6_lagged_df)  # Combine data frames

# Remove rows with NAs created by lagging
h6_final_data <- h6_final_data[complete.cases(h6_final_data), ]

# Define the forecasting horizon
forecast_horizon <- 6  # Update to horizon 6

train_inflation <- h6_final_data %>% filter(Date <= '2016-12-28')
missing_values <- sum(is.na(train_inflation))
# Want last 80 forecast to compare with other models
test_inflation <- h6_final_data %>% filter(Date >= '2017-05-28' & Date <= '2023-08-28')

# Define the time control for time series cross-validation
myTimeControl <- trainControl(
  method = "timeslice",
  initialWindow = 500,
  horizon = forecast_horizon,
  fixedWindow = TRUE,
  allowParallel = TRUE
)

# Define the formula for the model
formula <- as.formula("cpi ~ . - Date - Index - month")

# Train the Random Forest model
rf_model <- train(
  formula,
  data = train_inflation,
  method = "rf",
  trControl = myTimeControl,
  tuneGrid = expand.grid(mtry = 4),  # Adjust tuning parameters as needed
  metric = "RMSE",
  ntree = 100 
)

# Get forecasted values
rf_forecast6 <- predict(rf_model, newdata = test_inflation)

# Print Accuracy
accuracy(rf_forecast6, test_inflation$cpi)

# Calculate RMSE
rf_RMSE_h6 <- sqrt(mean((rf_forecast6 - test_inflation$cpi)^2))

# Print RMSE
print(paste("RMSE:", rf_RMSE_h6))
plot(test_inflation$cpi, type = "l")
lines(rf_forecast6, col = "red")

```

### RF Caret h=12

```{r}
# Load required libraries
library(caret)
library(randomForest)
library(dplyr)

# Create lag features for time series data for horizon 12
h12_lags <- 12:17  # Number of lags to consider for horizon 12
# Create lagged features for the CPI column
h12_lagged_data <- cbind(sapply(h12_lags, function(l) lag(inflation$cpi, l))) # Create lagged data

# Combine the lagged features into one data frame
h12_lagged_df <- data.frame(h12_lagged_data)
colnames(h12_lagged_df) <- paste0("h12_lag_", h12_lags)  # Rename columns with lag prefixes

# Merge the lagged features with the original data
h12_final_data <- bind_cols(inflation, h12_lagged_df)  # Combine data frames

# Remove rows with NAs created by lagging
h12_final_data <- h12_final_data[complete.cases(h12_final_data), ]

# Define the forecasting horizon
forecast_horizon <- 12  # Update to horizon 12

train_inflation <- h12_final_data %>% filter(Date <= '2016-12-28')
missing_values <- sum(is.na(train_inflation))
# Want last 80 forecast to compare with other models
test_inflation <- h12_final_data %>% filter(Date >= '2017-11-28' & Date <= '2023-08-28')

# Define the time control for time series cross-validation
myTimeControl <- trainControl(
  method = "timeslice",
  initialWindow = 500,
  horizon = forecast_horizon,
  fixedWindow = TRUE,
  allowParallel = TRUE
)

# Define the formula for the model
formula <- as.formula("cpi ~ . - Date - Index - month")

# Train the Random Forest model
rf_model <- train(
  formula,
  data = train_inflation,
  method = "rf",
  trControl = myTimeControl,
  tuneGrid = expand.grid(mtry = 4),  # Adjust tuning parameters as needed
  metric = "RMSE",
  ntree = 100 
)

# Get forecasted values
rf_forecast12 <- predict(rf_model, newdata = test_inflation)

# Print Accuracy
accuracy(rf_forecast12, test_inflation$cpi)

# Calculate RMSE
rf_RMSE_h12 <- sqrt(mean((rf_forecast12 - test_inflation$cpi)^2))

# Print RMSE
print(paste("RMSE:", rf_RMSE_h12))
plot(test_inflation$cpi, type = "l")
lines(rf_forecast12, col = "red")

```
### RF h=1/3/6/12 forecast in one variable rf_forecasts

```{r}
# Store rf_forecast1, rf_forecast3, rf_forecast6, and rf_forecast12 in rf_forecast
rf_forecasts <- list(
  `1` = rf_forecast1,
  `3` = rf_forecast3,
  `6` = rf_forecast6,
  `12` = rf_forecast12
)
```


##XGBoost with combination of hyperparameters

* I use different combination of hyper parameters in tuneGrid for the following code. And I got minimum RMSE for nrounds = 100, max_depth = 4,    eta (learning rate) = 0.1, gamma = 0.2 ( minimum loss reduction), colsample_bytree ( subsample ratio of columns) = 1, min_child_weight = 10,
 subsample = 0.8. So used this combination for h=1/3/6/12. Now I am commenting below code as it will take so much time to run.
 
```{r}
# # Load required libraries
# library(caret)
# library(randomForest)
# library(dplyr)
# 
# # Function to create lagged features
# create_lagged_features <- function(data, column, lags) {
#   lagged_data <- cbind(sapply(lags, function(l) lag(data[[column]], l)))
#   colnames(lagged_data) <- paste0(column, "_lag_", lags)
#   return(lagged_data)
# }
# 
# # Create lagged features for CPI column
# lags <- 1:6
# lagged_features <- create_lagged_features(inflation, "cpi", lags)
# 
# # Merge lagged features with original data
# final_data <- bind_cols(inflation, lagged_features)
# final_data <- final_data[complete.cases(final_data), ]
# 
# # Define training and testing data
# train_data <- final_data %>% filter(Date <= '2016-12-28')
# test_data <- final_data %>% filter(Date >= '2017-05-28' & Date <= '2023-08-28')
# 
# # Define time control for time series cross-validation
# myTimeControl <- trainControl(
#   method = "timeslice",
#   initialWindow = 500,
#   horizon = 1,
#   fixedWindow = TRUE,
#   allowParallel = TRUE
# )
# 
# # Define formula for the model
# formula <- as.formula("cpi ~ . - Date-Index-month")
# 
# # Tune hyperparameters more finely
# tuneGrid <- expand.grid(
#   nrounds = c(100, 200, 300),             # number of boosting rounds
#   max_depth = c(4, 6, 8),             # maximum depth of trees
#   eta = c(0.1, 0.2, 0.3),                 # learning rate
#   gamma = c(0, 0.1, 0.2),                 # minimum loss reduction required to make a further partition
#   colsample_bytree = c(0.6, 0.8, 1),    # subsample ratio of columns
#   min_child_weight = c(1, 5, 10),
#   subsample = c(0.6, 0.8, 1)              # subsample ratio of the training instances
# )
# 
# # Train XGBoost model with improved parameters
# xgb_model <- train(
#   formula,
#   data = train_data,
#   method = "xgbTree",
#   trControl = myTimeControl,
#   tuneGrid = tuneGrid,
#   metric = "RMSE"
# )
# # Get forecasted values
# forecast_values_xgb <- predict(xgb_model, newdata = test_data)
# 
# # Calculate RMSE
# rmse <- RMSE(forecast_values_xgb, test_data$cpi)
# 
# # Print RMSE
# print(paste("RMSE:", rmse))

```

### XGB h=1

```{r}
# Load required libraries
library(caret)
# Load required libraries
library(randomForest)
library(dplyr)

# Create lag features for time series data
h1_lags <- 1:6  # Number of lags to consider
# Create lagged features for the CPI column
h1_lagged_data <- cbind(sapply(h1_lags, function(l) lag(inflation$cpi, l))) # Create lagged data

# Combine the lagged features into one data frame
h1_lagged_df <- data.frame(h1_lagged_data)
colnames(h1_lagged_df) <- paste0("h1_lag_", h1_lags)  # Rename columns with lag prefixes

# Merge the lagged features with the original data
h1_final_data <- bind_cols(inflation, h1_lagged_df)  # Combine data frames

# Remove rows with NAs created by lagging
h1_final_data <- h1_final_data[complete.cases(h1_final_data), ]

# Define the forecasting horizon
forecast_horizon <- 1
train_inflation <- h1_final_data %>% filter(Date <= '2016-12-28')
test_inflation <- h1_final_data %>% filter(Date >= '2016-12-28' & Date <= '2023-08-28')

# Define the time control for time series cross-validation
myTimeControl <- trainControl(
  method = "timeslice",
  initialWindow = 500,
  horizon = forecast_horizon,
  fixedWindow = TRUE,
  allowParallel = TRUE
)

# Define the formula for the model
formula <- as.formula("cpi ~ . - Date")

# Define the tuning grid
tuneGrid <- expand.grid(
  nrounds = 100,             # number of boosting rounds
  max_depth = 4,             # maximum depth of trees
  eta = 0.1,                 # learning rate
  gamma = 0.2,                 # minimum loss reduction required to make a further partition
  colsample_bytree = 1,    # subsample ratio of columns
  min_child_weight = 10,
  subsample = 0.8              # subsample ratio of the training instances
)

# Train the XGBoost model
xgb_model <- train(
  formula,
  data = train_inflation,
  method = "xgbTree",
  trControl = myTimeControl,
  tuneGrid = tuneGrid,  
  metric = "RMSE"
)

# Get forecasted values
xgb_forecast1 <- predict(xgb_model, newdata = test_inflation)

cat('\n')
# Print or use forecasted values as needed
accuracy(xgb_forecast1, test_inflation$cpi)

# Calculate RMSE
xgb_rmse_h1 <- sqrt(mean((xgb_forecast1 - test_inflation$cpi)^2))

# Print RMSE
print(paste("RMSE:", xgb_rmse_h1))

```

###XGB h=3

```{r}
# Load required libraries
library(caret)
# Load required libraries
library(randomForest)
library(dplyr)

# Create lag features for time series data
h3_lags <- 3:8  # Number of lags to consider
# Create lagged features for the CPI column
h3_lagged_data <- cbind(sapply(h3_lags, function(l) lag(inflation$cpi, l))) # Create lagged data

# Combine the lagged features into one data frame
h3_lagged_df <- data.frame(h3_lagged_data)
colnames(h3_lagged_df) <- paste0("h3_lag_", h3_lags)  # Rename columns with lag prefixes

# Merge the lagged features with the original data
h3_final_data <- bind_cols(inflation, h3_lagged_df)  # Combine data frames

# Remove rows with NAs created by lagging
h3_final_data <- h3_final_data[complete.cases(h3_final_data), ]

# Define the forecasting horizon
forecast_horizon <- 3
train_inflation <- h3_final_data %>% filter(Date <= '2016-12-28')
test_inflation <- h3_final_data %>% filter(Date >= '2017-02-28' & Date <= '2023-08-28')

# Define the time control for time series cross-validation
myTimeControl <- trainControl(
  method = "timeslice",
  initialWindow = 500,
  horizon = forecast_horizon,
  fixedWindow = TRUE,
  allowParallel = TRUE
)

# Define the formula for the model
formula <- as.formula("cpi ~ . - Date")

# Define the tuning grid
tuneGrid <- expand.grid(
  nrounds = 100,             # number of boosting rounds
  max_depth = 4,             # maximum depth of trees
  eta = 0.1,                 # learning rate
  gamma = 0.2,                 # minimum loss reduction required to make a further partition
  colsample_bytree = 1,    # subsample ratio of columns
  min_child_weight = 10,
  subsample = 0.8              # subsample ratio of the training instances
)

# Train the XGBoost model
xgb_model <- train(
  formula,
  data = train_inflation,
  method = "xgbTree",
  trControl = myTimeControl,
  tuneGrid = tuneGrid,  
  metric = "RMSE"
)

# Get forecasted values
xgb_forecast3 <- predict(xgb_model, newdata = test_inflation)

cat('\n')
# Print or use forecasted values as needed
accuracy(xgb_forecast3, test_inflation$cpi)

# Calculate RMSE
xgb_rmse_h3 <- sqrt(mean((xgb_forecast3 - test_inflation$cpi)^2))

# Print RMSE
print(paste("RMSE:", xgb_rmse_h3))

```
### XGB h=6

```{r}
# Load required libraries
library(caret)
# Load required libraries
library(randomForest)
library(dplyr)

# Create lag features for time series data
h6_lags <- 6:11  # Number of lags to consider
# Create lagged features for the CPI column
h6_lagged_data <- cbind(sapply(h6_lags, function(l) lag(inflation$cpi, l))) # Create lagged data

# Combine the lagged features into one data frame
h6_lagged_df <- data.frame(h6_lagged_data)
colnames(h6_lagged_df) <- paste0("h6_lag_", h6_lags)  # Rename columns with lag prefixes

# Merge the lagged features with the original data
h6_final_data <- bind_cols(inflation, h6_lagged_df)  # Combine data frames

# Remove rows with NAs created by lagging
h6_final_data <- h6_final_data[complete.cases(h6_final_data), ]

# Define the forecasting horizon
forecast_horizon <- 6
train_inflation <- h6_final_data %>% filter(Date <= '2016-12-28')
test_inflation <- h6_final_data %>% filter(Date >= '2017-05-28' & Date <= '2023-08-28')

# Define the time control for time series cross-validation
myTimeControl <- trainControl(
  method = "timeslice",
  initialWindow = 500,
  horizon = forecast_horizon,
  fixedWindow = TRUE,
  allowParallel = TRUE
)

# Define the formula for the model
formula <- as.formula("cpi ~ . - Date")

# Define the tuning grid
tuneGrid <- expand.grid(
  nrounds = 100,             # number of boosting rounds
  max_depth = 4,             # maximum depth of trees
  eta = 0.1,                 # learning rate
  gamma = 0.2,                 # minimum loss reduction required to make a further partition
  colsample_bytree = 1,    # subsample ratio of columns
  min_child_weight = 10,
  subsample = 0.8              # subsample ratio of the training instances
)

# Train the XGBoost model
xgb_model <- train(
  formula,
  data = train_inflation,
  method = "xgbTree",
  trControl = myTimeControl,
  tuneGrid = tuneGrid,  
  metric = "RMSE"
)

# Get forecasted values
xgb_forecast6 <- predict(xgb_model, newdata = test_inflation)

cat('\n')
# Print or use forecasted values as needed
accuracy(xgb_forecast6, test_inflation$cpi)

# Calculate RMSE
xgb_rmse_6 <- sqrt(mean((xgb_forecast6 - test_inflation$cpi)^2))

# Print RMSE
print(paste("RMSE:", xgb_rmse_6))

```

### XGB h=12

```{r}
# Load required libraries
library(caret)
# Load required libraries
library(randomForest)
library(dplyr)

# Create lag features for time series data
h12_lags <- 12:17  # Number of lags to consider
# Create lagged features for the CPI column
h12_lagged_data <- cbind(sapply(h12_lags, function(l) lag(inflation$cpi, l))) # Create lagged data

# Combine the lagged features into one data frame
h12_lagged_df <- data.frame(h12_lagged_data)
colnames(h12_lagged_df) <- paste0("h12_lag_", h12_lags)  # Rename columns with lag prefixes

# Merge the lagged features with the original data
h12_final_data <- bind_cols(inflation, h12_lagged_df)  # Combine data frames

# Remove rows with NAs created by lagging
h12_final_data <- h12_final_data[complete.cases(h12_final_data), ]

# Define the forecasting horizon
forecast_horizon <- 12
train_inflation <- h12_final_data %>% filter(Date <= '2016-12-28')
test_inflation <- h12_final_data %>% filter(Date >= '2017-11-28' & Date <= '2023-08-28')

# Define the time control for time series cross-validation
myTimeControl <- trainControl(
  method = "timeslice",
  initialWindow = 500,
  horizon = forecast_horizon,
  fixedWindow = TRUE,
  allowParallel = TRUE
)

# Define the formula for the model
formula <- as.formula("cpi ~ . - Date")

# Define the tuning grid
tuneGrid <- expand.grid(
  nrounds = 100,             # number of boosting rounds
  max_depth = 4,             # maximum depth of trees
  eta = 0.1,                 # learning rate
  gamma = 0.2,                 # minimum loss reduction required to make a further partition
  colsample_bytree = 1,    # subsample ratio of columns
  min_child_weight = 10,
  subsample = 0.8              # subsample ratio of the training instances
)

# Train the XGBoost model
xgb_model <- train(
  formula,
  data = train_inflation,
  method = "xgbTree",
  trControl = myTimeControl,
  tuneGrid = tuneGrid,  
  metric = "RMSE"
)

# Get forecasted values
xgb_forecast12 <- predict(xgb_model, newdata = test_inflation)

cat('\n')
# Print or use forecasted values as needed
accuracy(xgb_forecast12, test_inflation$cpi)

# Calculate RMSE
xgb_rmse_h12 <- sqrt(mean((xgb_forecast12 - test_inflation$cpi)^2))

# Print RMSE
print(paste("RMSE:", xgb_rmse_h12))

```

###

```{r}
# Store xgb_forecast1, xgb_forecast3, xgb_forecast6, and xgb_forecast12 in xgb_forecast
xgb_forecasts <- list(
  `1` = xgb_forecast1,
  `3` = xgb_forecast3,
  `6` = xgb_forecast6,
  `12` = xgb_forecast12
)
```


```{r}
```